---
title: "ANOVA testing for climate variables"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include = FALSE}
library(tidyverse)
library(dplyr)
library(knitr)
```


```{r, include = FALSE}
fire_df = read_csv("./data/forestfires.csv")
fire_df
```


### Question we are answering:

Which climate variable has the largest effect on wild fire?

### Methods
The statistical test we used to answer this question is One-way ANOVA. The null hypothesis is that the mean of each variable in days with fire and without fire is the same. By conducting ANOVA tests for all climate variables with respect to fire status(fire/no fire), the following resulted tables were generated. If there is a significant difference between fire days and no fire days(the null hypothesis is rejected) for a certain variable, it can be inferred that the specific climate variable has no significant effect on wild fire.

```{r, include = FALSE}
fire_df_2 = 
  fire_df %>% 
  select(FFMC, DMC, DC, ISI, temp, RH, wind, rain, area) %>% 
  mutate(fire = ifelse(area > 0, "fire", "no fire"))
```

### FFMC Index

```{r, echo = FALSE}
# FFMC
fire_ffmc = 
  fire_df_2 %>%
  select(FFMC, fire)
anova_ffmc = lm(FFMC ~ factor(fire), data = fire_ffmc)
anova(anova_ffmc) %>% 
  kable()
```

**p-value > 0.05**
, we fail to reject the null hypothesis, and conclude that there is no significant difference between FFMC index and wild fire.

### DMC Index

```{r, echo = FALSE}
# DMC
fire_dmc = 
  fire_df_2 %>%
  select(DMC, fire)
anova_dmc = lm(DMC ~ factor(fire), data = fire_dmc)
anova(anova_dmc) %>% 
  kable()
```

**p-value > 0.05**
, we fail to reject the null hypothesis, and conclude that there is no significant difference between DMC index and wild fire.

### DC Index

```{r, echo = FALSE}
# DC
fire_dc = 
  fire_df_2 %>%
  select(DC, fire)
anova_dc = lm(DC ~ factor(fire), data = fire_dc)
anova(anova_dc) %>% 
  kable()
```

**p-value < 0.05**
, we reject the null hypothesis, and conclude that there is significant difference between DC index and wild fire.

### ISI Index

```{r, echo = FALSE}
# ISI
fire_isi = 
  fire_df_2 %>%
  select(ISI, fire)
anova_isi = lm(ISI ~ factor(fire), data = fire_isi)
anova(anova_isi) %>% 
  kable()
```

**p-value > 0.05**
, we fail to reject the null hypothesis, and conclude that there is no significant difference between ISI index and wild fire.

### Temperature

```{r, echo = FALSE}
# Temp
fire_temp = 
  fire_df_2 %>%
  select(temp, fire)
anova_temp = lm(temp ~ factor(fire), data = fire_temp)
anova(anova_temp) %>% 
  kable()
```

**p-value > 0.05**
, we fail to reject the null hypothesis, and conclude that there is no significant difference between temperature and wild fire.

### Relative Humidity

```{r, echo = FALSE}
# RH
fire_rh = 
  fire_df_2 %>%
  select(RH, fire)
anova_rh = lm(RH ~ factor(fire), data = fire_rh)
anova(anova_rh) %>% 
  kable()
```

**p-value > 0.05**
, we fail to reject the null hypothesis, and conclude that there is no significant difference between relative humidity and wild fire.

### Wind Speed

```{r, echo = FALSE}
# Wind
fire_wind = 
  fire_df_2 %>%
  select(wind, fire)
anova_wind = lm(wind ~ factor(fire), data = fire_wind)
anova(anova_wind) %>% 
  kable()
```

**p-value > 0.05**
, we fail to reject the null hypothesis, and conclude that there is no significant difference between wind speed and wild fire.

### Precipitation

```{r, echo = FALSE}
# Rain
fire_rain = 
  fire_df_2 %>%
  select(rain, fire)
anova_rain = lm(rain ~ factor(fire), data = fire_rain)
anova(anova_rain) %>% 
  kable()
```

**p-value > 0.05**
, we fail to reject the null hypothesis, and conclude that there is no significant difference between precipitation and wild fire.

