---
title: "Geography"

output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include = FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(patchwork)
library(plotly)
library(png)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

fire_df = read_csv("./data/forestfires.csv")
```

### Question trying to address in this section

* Where in the park has the most severe fire?

### Crude variables involved in this section

* X - x-axis spatial coordinate within the Montesinho park map: 1 to 9
* Y - y-axis spatial coordinate within the Montesinho park map: 2 to 9
* area - the burned area of the forest (in ha): 0.00 to 1090.84

### Description on plot

* From the website, we got the map of Montesinho Natural Park with axes. If the variables `X` and `Y`

### Geography plot

```{r x+y}
geo_1 = 
  fire_df %>% 
  select(X, Y, area) %>% 
  group_by(X, Y) %>% 
  mutate(total = sum(area)) %>% 
  select(-area) %>% 
  distinct() %>% 
  ungroup() 

geo_2 = 
  expand.grid(
    X = unique(pull(geo_1, X)),
    Y = unique(pull(geo_1, X))
  )

geo_3 = 
  merge(
    geo_2, geo_1, all = TRUE
  ) %>% 
  arrange(Y, X)

geo_4 = 
  geo_3 %>% 
  mutate(
    Y = -Y
  ) 

geo_4[is.na(geo_4)] <- 0

map_image = png::readPNG("map.png")

map_image_g = grid::rasterGrob(map_image, width = unit(0.89,"npc"), height = unit(0.89,"npc"))

overlap = 
  ggplot(geo_4, aes(X, Y, fill = total)) + 
  annotation_custom(map_image_g) +
  geom_tile() +
  theme_void() +
  theme(aspect.ratio = nrow(map_image)/ncol(map_image)) +
  scale_fill_gradient(low = "transparent", high = "red")

overlap
```