---
title: "Multiple Linear Modeling"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include = FALSE}
library(tidyverse)
library(dplyr)
library(broom)
library(modelr)
library(plotly)
library(ggplot2)
library(knitr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


```{r model, include = FALSE}
fire_linear = 
  read_csv("./data/forestfires.csv") %>% 
  select(FFMC, DMC, DC, ISI, temp, RH, wind, rain, area) %>% 
  filter(area > 0)
```

### Backward Elimination

Backward Elimination is conducted to select the possible predictors for linear regression. First is to start with a complete linear model with all predicting variables, and remove the predictor with the highest p-value(for which is greater than the threshold of 0.2). Then, refit the model and remove the next least significant predictor. Repeat the steps until all p-values are smaller than 0.2. The following tables show the first step with all predictors and the final step with confined predictors.

```{r, include = FALSE}
# complete model
fit = lm(area ~ FFMC + DMC + DC + ISI + temp + RH + wind + rain, data = fire_linear)
summary(fit)$coef %>% 
  as.data.frame() %>% 
  kable(caption = "Linear Model with All Predictors")

# -rain
fit2 = lm(area ~ FFMC + DMC + DC + ISI + temp + RH + wind, data = fire_linear)
summary(fit2)$coef

# -FFMC
fit3 = lm(area ~ DMC + DC + ISI + temp + RH + wind, data = fire_linear)
summary(fit3)$coef

# -DC
fit4 = lm(area ~ DMC + ISI + temp + RH + wind, data = fire_linear)
summary(fit4)$coef

# -temp
fit5 = lm(area ~ DMC + ISI + RH + wind, data = fire_linear)
summary(fit5)$coef

# -wind
fit6 = lm(area ~ DMC + ISI + RH, data = fire_linear)
summary(fit6)$coef

# -ISI
fit_best = lm(area ~ DMC + RH, data = fire_linear)
summary(fit_best)$coef %>% 
  as.data.frame() %>% 
  kable(caption = "Confined Linear Model with DMC and RH as predictors")


```

```{r, echo = FALSE}
fit = lm(area ~ FFMC + DMC + DC + ISI + temp + RH + wind + rain, data = fire_linear)
summary(fit)$coef %>% 
  as.data.frame() %>% 
  kable(caption = "Linear Model with All Predictors")

fit_best = lm(area ~ DMC + RH, data = fire_linear)
summary(fit_best)$coef %>% 
  as.data.frame() %>% 
  kable(caption = "Confined Linear Model with DMC and RH as predictors")

```


### Multiple Linear Regression

The final predictors selected are DMC and RH(Relative Humidity), which p-values are greater than our threshold of 0.2. Our hypothesized formula for MLR model is:
$$Burned Area = \beta_0 +\beta_1DMC + \beta_2RH$$
The coeffieicnts plot for DMC and RH is shown below:

```{r, echo = FALSE, warning = FALSE}
# plot for coefficients
model = 
  fit_best %>% 
  tidy() %>% 
  select(-std.error, -statistic)

coef_plot = 
  model %>% 
  filter(!term == "(Intercept)") %>% 
  mutate(
    text_label = str_c("Climate Variable: ", term, "\np-value: ", p.value)
  ) %>% 
  plot_ly(
    y = ~estimate, x = ~term, 
    text = ~text_label,
    type = "bar", color = "viridis"
  ) %>% 
  layout(
    title = "Coefficients for Each Climate Variable",
    xaxis = list(title = "Climate Variable"),
    yaxis = list(title = "Coefficient for Linear Model")
  )

coef_plot
```

It shows something that I dont want to write.


### Diagnostics

To examine the feasibility and accuracy of our model, plot of residuals was made. The residuals do not show a normal distribution, which indicates that the linear model utlized is not accurate and not appropriate for this dataset.
```{r}

# Residuals
add_residuals(fire_linear, lm(area ~ DMC + RH, data = fire_linear)) %>%
  plot_ly(
    y = ~resid, type = "violin"
  ) %>% 
  layout(
    title = "Boxplot for Residuals",
    xaxis = list(title = "Climate Variable"),
    yaxis = list(title = "Residual", range = c(-200, 300))
  )

```








